### 2007-02-09 Documentation/part1.tex
*** empty log message ***

\begin{quote}{\tt \footnotesize

double likelihood(double true\_rate, double fit\_rate, double sqr\_sigma) \\
\{ if (sqr\_sigma > 0) return square(true\_rate - fit\_rate) / sqr\_sigma; else return 0.0; \}

double chiDCNorm(int exp, int rule, int np, double *x, double *errors) \\
\{ \\
  \hspace*{0.3cm} const EXP\_FAR = 0; const EXP\_NEAR = 1; \\
  \hspace*{0.3cm} int n\_bins = glbGetNumberOfBins(EXP\_FAR); \\
  \hspace*{0.3cm} double *true\_rates\_N = glbGetRuleRatePtr(EXP\_NEAR, 0); \\
  \hspace*{0.3cm} double *true\_rates\_F = glbGetRuleRatePtr(EXP\_FAR, 0); \\
  \hspace*{0.3cm} double signal\_fit\_rates\_N[n\_bins]; double signal\_fit\_rates\_F[n\_bins]; \\
  \hspace*{0.3cm} double signal\_norm\_N, signal\_norm\_F; \\
  \hspace*{0.3cm} int ew\_low, ew\_high, i; \\
  \hspace*{0.3cm} double emin, emax, fit\_rate;  double chi2 = 0.0;

@@

User-defined systematics is, compared to the built-in systematics, a compound between
the \AEDL\ definition and some source code defining the behavior. In the simplest case,
the \AEDL\ file defines user-defined systematics for a specific rule, gives it a 
name/identifier, and defines the systematical errors. The source code has then to match this \AEDL\
definition -- therefore, make sure to use only unique identifiers. 
Ones needs to register the user-defined systematics in the 
source code (typically after {\tt glbInit}) with
\begin{function}
\GLBNS{DefineChiFunction}
{\tt int glbDefineChiFunction(glb\_chi\_function chi\_func, int dim, const char *name, void* user\_data)}
 tells \GLOBES\ to register the user-defined systematics $\chi^2$ function {\tt chi\_func} 
identified by the string {\tt name} with {\tt dim} systematics parameters. The parameter {\tt user\_data}
is an arbitrary pointer being transferred to {\tt chi\_func}. It can, for instance, be used to avoid
global variables. Returns zero, if successful.
\end{function}
The user-defined systematics function itself has to have the pre-defined type 
\begin{function}
\GLBNS{\_chi\_function}
{\tt double (*glb\_chi\_function)(int exp, int rule, int dim, double *params, double *errors, void* user\_data)}.
In this function type, {\tt exp} is the experiment number, {\tt rule} is the rule number, {\tt dim} is the number of systematics parameters, {\tt params} is an array of the systematics nuisance parameters themselves, and {\tt errors} is an array with the systematical errors. The parameter {\tt user\_data} is set as defined with
{\tt glbDefineChiFunction}.
Note the the central values for {\tt params} are $0$, which means that $0$ corresponds to the un-modified rates. The array indices run from $0$ to {\tt dim}-1.
\end{function}
Note that this function will be called many times by the \GLOBES\ minimizers.
Therefore the function should be as efficient as possible.
%JK - THIS IS INCORRECT: ONE MINIMIZATION OVER, SAY, 8 PARAMETERS IS FASTER THAN
%2 MINIMIZATIONS OVER 4 PARAMETERS EACH-
%In many cases, it is also recommendable to use different functions for different
%rules, since the fewer auxiliary parameters in the minimization, the faster the routine will be.
In addition, note that complicated systematics with many parameters may introduce complicated (unknown) topologies for the minimization, which means that the minimizers may
end up in a local minimum instead of the global minimum. \GLOBES\ provides the function \GLB{SetSysStartingValuesList} to change the starting values of the minimizer in the case of
 convergence problems (see below).
A typical implementation may look like the following code, where ``{\tt chiDCNorm}'' is the identifier
assigned in the \AEDL\ definition:
\begin{quote}
{\tt
  double chiDCNorm(int exp, int rule, int dim, double *x, \\
  \hspace*{0.5cm} double *errors) \\
  \{ \\
   \hspace*{0.5cm} double chi2 = 0.0; \\
   \hspace*{0.5cm} int i; \\
   \\
   \hspace*{0.5cm} ... /* Some code to calculate the chi2 */ \\
   \\
    \hspace*{0.5cm} /* Here the systematics priors (penalties) are added: */ \\
    \hspace*{0.5cm} for(i=0;i<dim;i++) chi2 += (x[i]*x[i])/(errors[i]*errors[i]);
    \hspace*{0.5cm} return chi2; \\
  \} \\
   \\
  int main(int argc,char*argv[]) \\
 \{ \\ 
  \hspace*{0.5cm} ... \\
  \hspace*{0.5cm} glbInit(agrv[0]); \\
  \hspace*{0.5cm} glbDefineChiFunction(\&chiDCNorm,5,"chiDCNorm"); \\
  \hspace*{0.5cm} ... \\
 \} \\
}
\end{quote}

@@

\hspace*{0.5cm}        @sys\_on\_errors    = \{ 0.02,    0.006,        0.006,       0.005,     0.005   \} \\

>>>>

\vspace*{-0.3cm}

\begin{quote}{\tt \footnotesize
double likelihood(double true\_rate, double fit\_rate, double sqr\_sigma) \\
\{ if (sqr\_sigma > 0) return square(true\_rate - fit\_rate) / sqr\_sigma; else return 0.0; \}

double chiDCNorm(int exp, int rule, int np, double *x, double *errors, \\
  \hspace*{0.3cm}  void* user\_data) \\
\{ \\
  \hspace*{0.3cm} const EXP\_FAR = 0; const EXP\_NEAR = 1; \\
  \hspace*{0.3cm} int n\_bins = glbGetNumberOfBins(EXP\_FAR); \\
  \hspace*{0.3cm} double *true\_rates\_N = glbGetRuleRatePtr(EXP\_NEAR, 0); \\
  \hspace*{0.3cm} double *true\_rates\_F = glbGetRuleRatePtr(EXP\_FAR, 0); \\
  \hspace*{0.3cm} double signal\_fit\_rates\_N[n\_bins]; double signal\_fit\_rates\_F[n\_bins]; \\
  \hspace*{0.3cm} double signal\_norm\_N, signal\_norm\_F; \\
  \hspace*{0.3cm} int ew\_low, ew\_high, i; \\
  \hspace*{0.3cm} double emin, emax, fit\_rate;  double chi2 = 0.0;

@@

User-defined systematics is, compared to the built-in systematics, a compound between
the \AEDL\ definition and some source code defining the behavior. In the simplest case,
the \AEDL\ file defines user-defined systematics for a specific rule, gives it a 
name/identifier, and defines the systematical errors. The source code has then to match this \AEDL\
definition -- therefore, make sure to use only unique identifiers. 
Ones needs to register the user-defined systematics in the 
source code (typically after {\tt glbInit}) with
\begin{function}
\GLBNS{DefineChiFunction}
{\tt int glbDefineChiFunction(glb\_chi\_function chi\_func, int dim, const char *name, void* user\_data)}
 tells \GLOBES\ to register the user-defined systematics $\chi^2$ function {\tt chi\_func} 
identified by the string {\tt name} with {\tt dim} systematics parameters. The parameter {\tt user\_data}
is an arbitrary pointer being transferred to {\tt chi\_func}. It can, for instance, be used to avoid
global variables. Returns zero, if successful.
\end{function}
The user-defined systematics function itself has to have the pre-defined type 
\begin{function}
\GLBNS{\_chi\_function}
{\tt double (*glb\_chi\_function)(int exp, int rule, int dim, double *params, double *errors, void* user\_data)}.
In this function type, {\tt exp} is the experiment number, {\tt rule} is the rule number, {\tt dim} is the number of systematics parameters, {\tt params} is an array of the systematics nuisance parameters themselves, and {\tt errors} is an array with the systematical errors. The parameter {\tt user\_data} is set as defined with
{\tt glbDefineChiFunction}.
Note the the central values for {\tt params} are $0$, which means that $0$ corresponds to the un-modified rates. The array indices run from $0$ to {\tt dim}-1.
\end{function}
Note that this function will be called many times by the \GLOBES\ minimizers.
Therefore the function should be as efficient as possible.
%JK - THIS IS INCORRECT: ONE MINIMIZATION OVER, SAY, 8 PARAMETERS IS FASTER THAN
%2 MINIMIZATIONS OVER 4 PARAMETERS EACH-
%In many cases, it is also recommendable to use different functions for different
%rules, since the fewer auxiliary parameters in the minimization, the faster the routine will be.
In addition, note that complicated systematics with many parameters may introduce complicated (unknown) topologies for the minimization, which means that the minimizers may
end up in a local minimum instead of the global minimum. \GLOBES\ provides the function \GLB{SetSysStartingValuesList} to change the starting values of the minimizer in the case of
 convergence problems (see below).
A typical implementation may look like the following code, where ``{\tt chiDCNorm}'' is the identifier
assigned in the \AEDL\ definition:
\begin{quote}
{\tt
  double chiDCNorm(int exp, int rule, int dim, double *x, \\
  \hspace*{0.5cm} double *errors, void* user\_data) \\
  \{ \\
   \hspace*{0.5cm} double chi2 = 0.0; \\
   \hspace*{0.5cm} int i; \\
   \\
   \hspace*{0.5cm} ... /* Some code to calculate the chi2 */ \\
   \\
    \hspace*{0.5cm} /* Here the systematics priors (penalties) are added: */ \\
    \hspace*{0.5cm} for(i=0;i<dim;i++) chi2 += (x[i]*x[i])/(errors[i]*errors[i]);
    \hspace*{0.5cm} return chi2; \\
  \} \\
   \\
  int main(int argc,char*argv[]) \\
 \{ \\ 
  \hspace*{0.5cm} ... \\
  \hspace*{0.5cm} glbInit(agrv[0]); \\
  \hspace*{0.5cm} glbDefineChiFunction(\&chiDCNorm,5,"chiDCNorm",NULL); \\
  \hspace*{0.5cm} ... \\
 \} \\
}
\end{quote}

@@

\hspace*{0.5cm}        @sys\_on\_errors    = \{ 0.028,    0.006,        0.006,       0.005,     0.005   \} \\
